Estimation and Implications of Bias in EPA Pollution Measurement

### 2022-04-04 paper/ongoing_progress/progress_2022-03-18.tex

%---------------------------------------------------------
%This block of code is for the table of contents after
%the title page
\begin{frame}
\frametitle{Motivation}
\textbf{Clean Air}

\begin{itemize}
    \item The Clean Air Act (1970) established National Ambient Air Quality Standards
    (NAAQS) for US counties
    \item Either "attainment" or "non-attainment", penalties/forced adoption
    \item Minimum requirement of 75\% of readings, per quarter
    \item Air quality can change quickly
    \item Monitor shutoffs are common
\end{itemize}
\vspace{2em}
\textbf{Research Questions}
\begin{itemize}
\item How biased are EPA monitor-based measures of local air quality?
\item Does this bias significantly change NAAQS attainment status?
\end{itemize}

@@

%---------------------------------------------------------
\begin{frame}
\frametitle{EPA National Ambient Air Quality Standards Monitors}

\includegraphics[width=\textwidth]{output/figures/epa/combined_uc_cali_epa.png}
\end{frame}

@@

%---------------------------------------------------------
%Example of the \pause command
\begin{frame}
\frametitle{National Ambient Air Quality Standards for PM2.5}
Two standards for assessing compliance for ambient PM2.5 concentrations at the location of a monitor:
\vspace{2em}

\textbf{Daily Design Value} (average)
\begin{itemize}
    \item[$\Rightarrow$] 3-year rolling average of 1-year average of daily averages
    \item[$\Rightarrow$] standard currently set at 15.0 $\mu$g/m$^3$
\end{itemize}
\vspace{1em}

\textbf{24-Hour Design Value} (98$^{th}$ percentile)
\begin{itemize}
    \item[$\Rightarrow$] 3-year rolling average of 1-year 98$^{th}$ percentile of daily averages
    \item[$\Rightarrow$] standard currently set at 35 $\mu$g/m$^3$
\end{itemize}
\end{frame}
%---------------------------------------------------------

%---------------------------------------------------------
%Highlighting text
\begin{frame}
\frametitle{NAAQS Completeness Criteria for daily monitors}

\textbf{Valid day:}
minimum of 75\% hours reported  (18 hours)

\vspace{2em}
\textbf{Valid quarter:}
minimum of 75\% valid days  (22-23 days\footnote{fewer for monitors that report less frequent observations})

\vspace{2em}
\textbf{Valid quarterly design value:}
all 12 quarters in 3-year period (12 quarters)

%---------------------------------------------------------
%Observed EPA Completeness
\begin{frame}
\frametitle{Observed Completeness of NAAQS Monitors in sample}
\includegraphics[width=0.8\textwidth]{example-image-a}
\end{frame}
%---------------------------------------------------------

>>>>

%---------------------------------------------------------
%This block of code is for the table of contents after
%the title page
\begin{frame}
\frametitle{State of project}
\textbf{Data (2016-2021)}

\begin{itemize}
    \item have: 15 CA EPA sites
    \item have: all hourly data for PA sites within 50 miles of all 15 EPA sites
    \item want: all US PA data
    \item can before April 11: get 10-50 more EPA sites
\end{itemize}
\vspace{2em}
\textbf{Analysis}
\begin{itemize}
\item have: Inverse distance weighted mean of PA
\item have: OLS to predict EPA with PA, give prediction intervals\\
$EPA_t = \beta_0 + \beta_1 PA^{IDW}_t + \varepsilon_t
$
\item want: prediction (1): more complicated OLS with windspeed and direction
\item prediction (2): machine learning model
\item can before April 11: probably windspeed and direction model
\end{itemize}

@@

%---------------------------------------------------------
\begin{frame}
\frametitle{Data Use Agreement}

\begin{itemize}
    \item Gave Adrian Dybwad draft person DUA
    \item Adrian said legal folks ask if we could do this at the University level
    \item I asked if we could do a temporary DUA while we get the university level one figured out
\end{itemize}

What are the first steps to getting a university level DUA?

\end{frame}

@@

% %---------------------------------------------------------
% %Example of the \pause command
% \begin{frame}
% \frametitle{National Ambient Air Quality Standards for PM2.5}
% Two standards for assessing compliance for ambient PM2.5 concentrations at the location of a monitor:
% \vspace{2em}

% \textbf{Daily Design Value} (average)
% \begin{itemize}
%     \item[$\Rightarrow$] 3-year rolling average of 1-year average of daily averages
%     \item[$\Rightarrow$] standard currently set at 15.0 $\mu$g/m$^3$
% \end{itemize}
% \vspace{1em}

% \textbf{24-Hour Design Value} (98$^{th}$ percentile)
% \begin{itemize}
%     \item[$\Rightarrow$] 3-year rolling average of 1-year 98$^{th}$ percentile of daily averages
%     \item[$\Rightarrow$] standard currently set at 35 $\mu$g/m$^3$
% \end{itemize}
% \end{frame}
% %---------------------------------------------------------

% %---------------------------------------------------------
% %Highlighting text
% \begin{frame}
% \frametitle{NAAQS Completeness Criteria for daily monitors}

% \textbf{Valid day:}
% minimum of 75\% hours reported  (18 hours)

% \vspace{2em}
% \textbf{Valid quarter:}
% minimum of 75\% valid days  (22-23 days\footnote{fewer for monitors that report less frequent observations})

% \vspace{2em}
% \textbf{Valid quarterly design value:}
% every in 3-year period
% (12 quarters)

% \end{frame}
% %---------------------------------------------------------

%---------------------------------------------------------
%Observed EPA Completeness
\begin{frame}
\frametitle{Observed Completeness of NAAQS Monitors in sample}
\includegraphics[width=\textwidth]{output/figures/epa_vs_pa/completeness/completeness_epa_pa.png}
\end{frame}
%---------------------------------------------------------
